---
title: Profile
author: jonthelaion
date: '2018-01-01'
slug: profile
categories:
  - profile
tags:
  - profile
---

# About Me

jon. sydney. australia. hokkien. chinese. earthling. dreamer. lefty. penspinner. nerd. early bird. night owl. afternoon zombie. book sniffer. star&cloudgazer. gamefreak. basketball. old fashioned. retro lover. walking anachronism. tree climber. amatog.

I believe

* that beauty is more than skin deep
* that chivalry ain’t dead
* that family is not just defined by blood
* that in the sky, there is no distinction of east or west
* that buddhism is more of a philosophy than a religion
* that pluto is a planet
* that cheez tv was the greatest show ever
* that simplicity is the ultimate sophistication

# Purpose

To observe, capture and understand the complexities of life;  
Express these complexities in a manner that is elegant in its simplicity;  
Thereby creating environments which are genuine, inspiring and fun;  
And ultimately making the world a better place as a result of my actions.

# Skills

Here is a self-assessment of my skills in line with the areas outlined in <a href="https://jonthelaion.rbind.io/post/doing-data-science-book/" target="_blank">Doing Data Science</a>.

```{r echo=FALSE}
library(ggplot2)
```

```{r echo=FALSE}
profile_df <- data.frame(cbind(c('Computer Science', 'Math', 'Statistics', 'Machine Learning', 'Domain Expertise', 'Communication and Presentation Skills', 'Data Visualisation'),c(0,1,1,0,2,2,2)))
names(profile_df) <- c('Area','Rating')
ggplot(profile_df, aes(x=Area, y=Rating)) +
    geom_col()
```
